On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-27 Manuscript/manuscript.tex
comments on graphs and calibration

\jy{Are the results from exponential margins the same? If so, we can put them in
  an appendix; make sure we have the data generation process accurately
  described. Then briefly summarize and refer to it at the end of the simulation
  section.} \mc{addressed}

\jy{The 80-width is for maximum. No need to re-wrap shorter lines because it
  would show a lot of diff while there is no diff.}
\mc{addressed}

@@

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap - 
originated by \citet{efron1979bootstrap} - but for serially dependent data.
\mc{style guide says to have citations after punctuation, not sure what to do 
with textual citations}
Early ideas of block
bootstrap were developed not long after the standard 
bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
has since
been applied in various fields, for instance, econometrics and 
meteorology.\citep{mackinnon2006bootstrap, varga2017generalised}
Block bootstrap is especially useful for serially dependent data when the serial 
dependence is not specified or not of primary interest. The method is expected 
to produce CIs with coverage rates matching their nominal levels as the sample 
size grows. However, when dealing with finite sample sizes, an important 
question is how large the sample size must be for block bootstrap CIs to have 
the desired coverage rates.

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$, 
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
of $Z_j$'s with replacement and then align them in the order they were picked to 
form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last block 
selected will be reduced in size so that the final size of the block bootstrap 
sample is $n$. It is also possible to implement moving block bootstrap while 
allowing blocks to wrap around the end of the series. In other words, define 
moving blocks (assuming $l > 1$) as:
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
This version does not require that $n/l$ be an integer.

@@

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let 
\begin{equation}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation}
Define
\begin{equation}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation}
and
\begin{equation}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\subsection*{Design}
We designed a simulation study to compare the performance of the different block 
bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

@@

\jy{The fonts of labels/annotatios in these figures are too big compared to the
  captions. Try pointsize = 9. The plots also seem oversized. Generate them in R
  with the right size in mind.} \mc{addressed}

@@

@@

For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$.

For estimating the standard deviation parameter~$\sigma_x$,
\textbf{Figure~\ref{fig:sigma}} suggests that every method can reach nominal 
coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
$\phi$, coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general.
Like $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample 
sizes when compared to other methods. Unlike $\mu$, there is no over-coverage 
issue for $\sigma_x$ when $\phi = -0.4$. Standard, percentile, BC, BCA, and 
recentered percentile CIs again have similar performance. All methods seem to 
have slightly higher coverage of $\sigma_x$ when $\phi$ is negative versus when 
$\phi$ is positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as 
the strength of the temporal dependence increases.

For estimating the autocorrelation parameter~$\phi$, 
\textbf{Figure~\ref{fig:phi}} suggests that while standard, Student's $t$, and 
recentered percentile CIs do approach correct coverage as sample size increases, 
percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
the strength of the temporal dependence increases. Because of this, only 
standard, Student's $t$, and recentered percentile CIs should be considered as 
effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
again can achieve correct coverage with smaller sample sizes when compared to 
standard and recentered percentile CIs which perform similarly. Student's $t$ 
CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
for all methods when the dependence is negative rather than positive. Whether or 
not the dependence is negative or positive, coverage of $\phi$ seems to increase 
slightly as the absolute value increases for standard, Student's $t$, and 
recentered percentile CIs. For the values of $\phi$ observed, there are no 
examples of over-coverage for standard, Student's $t$, BC, BCA, or recentered 
percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
should not be used.

@@

\jy{Could do one for the exponential margin study too. 
Maybe for the negative dependence.}
\mc{created negative dependence plots not included in manuscript yet}

@@

Block bootstrap is a useful method for estimating parameters of a time series,
from simple parameters like the mean to more complicated temporal dependence
factors. We know theoretically that the block bootstrap procedure will cover a 
parameter of a time series at the nominal level given an infinitely large 
sample, so the goal for this study was to find the smallest finite sample length 
$n$ of a time series in order for the block bootstrap procedure to recover its 
associated parameters at an acceptable rate. Our analysis relies on the 
assumption that there is a size $n$ large enough for the method to work: that 
is, the method's performance improves as $n$ increases. Out of the six types of 
intervals used in this study, this assumption was found to hold true with 
respect to estimating $\phi$ only for standard, Student's $t$, and recentered 
percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
deterioration as $n$ increased. The percentile CI's coverage deterioration can 
be attributed to bias that is not corrected as $n$ increases. Specifically, as 
$n$ increases, the width of the CI decreases, but because the percentile CI 
underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
bias, but the width of the CI seems to be inconsistent. The acceleration factor 
of the BCA CI seems to fail, as the width of the CI seems to be inconsistent.

@@

\appendix

\section*{Simulation Study with Exponential Marginal Distribution}

\jy{Motivation; data generation (calibration of copula parameters to give the
  desired rho); simulation design; plots; brief discussion of results.}
\mc{addressed}

This appendix concerns the performance of block bootstrap when used to estimate
the mean, standard deviation, and the lag-1 autocorrelation coefficient of a 
AR(1) process with an underlying exponential marginal distribution. The 
motivation for this additional simulation study was to observe if the results of 
the main simulation study will change if the underlying marginal distribution is
not normal.

We generated time series $X_t$ from a 1st order autoregressive 
(AR(1)) process as we did previously, but transformed the data from a standard
normal distribution to an exponential distribution with rate $\lambda = 1$, so 
that for $t \in \{1, \ldots, n\}$, we can define:
\begin{equation}
W_t = F^{-1}(\Phi(X_t), 1)
\end{equation}
where $F^{-1}(p, \lambda)$ is the quantile function for the exponential 
distribution with rate parameter $\lambda$.

The simulation design was the same, except the target parameters of $W_t$ were:
1) $\mu = 1$, the mean of $W_t$;
2) $\sigma_w = 1$, the standard deviation of $W_t$; and
3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$
Although we may have set $\phi$ to these five levels for $X_t$: 
$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
the new five true autocorrelation coefficients for $W_t$ were different.
\mc{I may need some help explaining the calibration of copula parameters}
To calibrate the copula parameters, we first constructed a multivariate
exponential distribution from a normal copula using the \textsl{copula} package.
\citep{copula} Then we computed $E[XY]$, which 
requires double integration using the \textsl{pracma} package. \citep{pracma} 
Finally, we obtained true $\rho = E[XY] - 1$, which was used as the target
parameter when evaluating CI performance when estimating $\rho$.
After this step, we again plotted empirical coverage 
rates for $\mu$, $\sigma$, and $\rho$, as well as 95\% confidence intervals of 
the real coverage. These are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.

@@

Although there are differences in the ranges of sample sizes needed to cover 
parameters of a normally distributed AR(1) process versus an exponentially 
distributed AR(1) process, the trends and patterns are generally the same.
Student's $t$ CIs still appear to yield higher coverage rates than other 
methods. Performance is still generally better when temporal dependence is 
negative rather than positive. Most importantly, percentile, BC, and BCA CIs
still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
in \textbf{Figure~\ref{fig:eri}}, percentile and BC CIs still have the same bias
issue.

>>>>

@@

Block bootstrap is a tool to construct confidence intervals (CI) to make
inferences about dependent data. Essentially, it depends on correct estimation
of the uncertainty in the estimation, similar to the standard bootstrap 
\citep{efron1979bootstrap}, but for serially dependent data.
Early ideas of block bootstrap were developed not long after the standard 
bootstrap.\citep{hall1985resampling, carlstein1986use,kunsch1989jackknife} It 
has since
been applied in various fields, for instance, econometrics and 
meteorology.\citep{mackinnon2006bootstrap, varga2017generalised}
Block bootstrap is especially useful for serially dependent data when the serial 
dependence is not specified or not of primary interest. The method is expected 
to produce CIs with coverage rates matching their nominal levels as the sample 
size grows. However, when dealing with finite sample sizes, an important 
question is how large the sample size must be for block bootstrap CIs to have 
the desired coverage rates.

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks
\[
Z_j = \{X_j, \ldots, X_{j + l - 1}\}, \quad, 
j = 1, \ldots, n - l + 1.
\]
Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
of $Z_j$'s with replacement and then align them in the order they were picked to 
form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last block 
selected will be reduced in size so that the final size of the block bootstrap 
sample is $n$. It is also possible to implement moving block bootstrap while 
allowing blocks to wrap around the end of the series. In other words, define 
moving blocks (assuming $l > 1$) as:
\begin{equation*}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & \text{if } j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation*}
This version does not require that $n/l$ be an integer.

@@

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let \jy{No need to number an equation if it is not referred to}
\begin{equation*}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation*}
Define
\begin{equation*}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation*}
and
\begin{equation*}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation*}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\subsection*{Design}
We designed a simulation study to compare the performance of the different block 
bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation*}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

@@

@@

\jy{I like the font size of the labels and axis of Figure 4. They are still
  overly large in Figures 1--3. The panel head is also too wide. The axis ticks
  look crowded. The panel
  labels on the right also does not look pretty. I'd prefer the old version if
  the font sizes were smaller.}

@@

\jy{Is textbf of Figure requried? Never manual formatting.}
For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$.

For estimating the standard deviation parameter~$\sigma_x$,
\textbf{Figure~\ref{fig:sigma}} suggests that every method can reach nominal 
coverage of $\sigma_x$ if the sample is large enough, but for a given $n$ and 
$\phi$, coverage of $\sigma_x$ will be lower than coverage of $\mu$ in general.
Like $\mu$, $\sigma_x$ can be covered by Student $t$ CIs with smaller sample 
sizes when compared to other methods. Unlike $\mu$, there is no over-coverage 
issue for $\sigma_x$ when $\phi = -0.4$. Standard normal, percentile, BC, BCA, and 
recentered percentile CIs again have similar performance. All methods seem to 
have slightly higher coverage of $\sigma_x$ when $\phi$ is negative versus when 
$\phi$ is positive. Regardless of the sign, coverage of $\sigma_x$ gets worse as 
the strength of the temporal dependence increases.

For estimating the autocorrelation parameter~$\phi$, 
\textbf{Figure~\ref{fig:phi}} suggests that while standard normal, Student's $t$, and 
recentered percentile CIs do approach correct coverage as sample size increases, 
percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
the strength of the temporal dependence increases. Because of this, only 
standard normal, Student's $t$, and recentered percentile CIs should be considered as 
effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
again can achieve correct coverage with smaller sample sizes when compared to 
standard and recentered percentile CIs which perform similarly. Student's $t$ 
CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
for all methods when the dependence is negative rather than positive. Whether or 
not the dependence is negative or positive, coverage of $\phi$ seems to increase 
slightly as the absolute value increases for standard normal, Student's $t$, and 
recentered percentile CIs. For the values of $\phi$ observed, there are no 
examples of over-coverage for standard normal, Student's $t$, BC, BCA, or recentered 
percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
should not be used.

@@

@@

Block bootstrap is a useful method for estimating parameters of a time series,
from simple parameters like the mean to more complicated temporal dependence
factors. We know theoretically that the block bootstrap procedure will cover a 
parameter of a time series at the nominal level given an infinitely large 
sample, so the goal for this study was to find the smallest finite sample length 
$n$ of a time series in order for the block bootstrap procedure to recover its 
associated parameters at an acceptable rate. Our analysis relies on the 
assumption that there is a size $n$ large enough for the method to work: that 
is, the method's performance improves as $n$ increases. Out of the six types of 
intervals used in this study, this assumption was found to hold true with 
respect to estimating $\phi$ only for standard normal, Student's $t$, and recentered 
percentile CIs, whereas percentile, BC, and BCA intervals exhibited coverage 
deterioration as $n$ increased. The percentile CI's coverage deterioration can 
be attributed to bias that is not corrected as $n$ increases. Specifically, as 
$n$ increases, the width of the CI decreases, but because the percentile CI 
underestimates $\phi$, the coverage decreases. The BC CI seems to correct the 
bias, but the width of the CI seems to be inconsistent. The acceleration factor 
of the BCA CI seems to fail, as the width of the CI seems to be inconsistent.

@@

\section*{Appendix: Simulation Study with Exponential Marginal Distribution}

This appendix concerns the performance of block bootstrap when used to estimate
the mean, standard deviation, and the lag-1 autocorrelation coefficient of a 
AR(1) process with an underlying unit exponential marginal distribution. The
motivation for this additional simulation study was to observe if the results of 
the main simulation study will change if the underlying marginal distribution is
not normal.

We generated time series $X_t$ from a 1st order autoregressive 
(AR(1)) process as we did previously, but transformed the data from a standard
normal distribution to an exponential distribution with rate $\lambda = 1$, so 
that for $t \in \{1, \ldots, n\}$, we can define:
\begin{equation*}
W_t = F^{-1}(\Phi(X_t), 1)
\end{equation*}
where $F^{-1}(p, \lambda)$ is the quantile function for the exponential 
distribution with rate parameter $\lambda$.

The simulation design was the same, except the target parameters of $W_t$ were:
1) $\mu = 1$, the mean of $W_t$;
2) $\sigma_w = 1$, the standard deviation of $W_t$; and
3) $\rho$, the lag-1 autocorrelation coefficient of $W_t$
Although we may have set $\phi$ to these five levels for $X_t$: 
$\{-0.4, -0.2, 0.0, 0.2, 0.4\}$, because of the transformation,
the new five true autocorrelation coefficients for $W_t$ were different.
\mc{I may need some help explaining the calibration of copula parameters}

To calibrate the copula parameters, we first constructed a multivariate
exponential distribution from a normal copula using the \textsl{copula} package.
\citep{copula} Then we computed $E[XY]$, which 
requires double integration using the \textsl{pracma} package. \citep{pracma} 
Finally, we obtained true $\rho = E[XY] - 1$, which was used as the target
parameter when evaluating CI performance when estimating $\rho$.
After this step, we again plotted empirical coverage 
rates for $\mu$, $\sigma$, and $\rho$, as well as 95\% confidence intervals of 
the real coverage. These are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.

\jy{Let $\rho$ and $\phi$ be the autocorrelation coefficient of $X_t$ and $W_t$,
  respectively. There is a 1-1 map between $\rho$ to $\phi$. You already figured
  out how to transform from $\rho$ to $\phi$. Now we want $\phi$ to be, say,
  0.4, you can calibrate $\rho$ to give you the desired value. This only need to
  be done once before your run your simulation. }

\jy{cite the copula book instead of the package}

\jy{comment on the similarity of the results with those reported in the main text.}

@@

Although there are differences in the ranges of sample sizes needed to cover 
parameters of a normally distributed AR(1) process versus an exponentially 
distributed AR(1) process, the trends and patterns are generally the same.
Student's $t$ CIs still appear to yield higher coverage rates than other 
methods. Performance is still generally better when temporal dependence is 
negative rather than positive. Most importantly, percentile, BC, and BCA CIs
still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
in Figure~\ref{fig:eri}, percentile and BC CIs still have the same bias
issue.
